---
title: "@reprosci"
output: github_document
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
##  a.k.a Reproducible science

The objective is to make the code available that allows the figures at @reprosci (https://twitter.com/reprosci) to be reproduced using raw data as distrbuted by the relavant authorities. Some caveats may apply, where the raw data has been prepocessed and condensed in order to manage compute resources. All code is strictly open source. In most cases, data processing and visualisation is achieved using ```r```, and relies on the ```RStudio``` environment, which is strongly recommended. Some simulations employ other codes, such as ```Basilisk```.

#### Procedure

The easist way to download the ```reprosci``` github repo  is to use the ```terminal```. The Following applies for the ```bash``` shell.

```{bash, echo=T, eval=F}
export DOWNLOAD_PATH=~/Downloads #change path to whatever directory you want
cd $DOWNLOAD_PATH 
git clone  https://github.com/msandifo/reprosci.git
```

My repro repo's  are typcially identified by year (e.g. ```2018```) and number (e.g. ```001```), sometimes with a prefix (e.f. ```repro001```)

#### Example - repro ```2018/reprosci001```

in ```terminal```
```{bash, echo=T, eval=F}
cd $DOWNLOAD_PATH/reprosci/2018/reprosci001  
rm -r .drake 
open reprosci001.Rproj 
```
In ```rstudio console```
```{r, echo=T, eval=F}
source("drake.R")
```

A full ```repro``` can be achieved by setting the ```full.repro=TRUE``` prior to  ```source("drake.R")```. This ensures downloads of relevant datasets and  full processing, as per ```./src/downloads.R```. T
```{r, echo=T, eval=F}
full.repro=TRUE
source("drake.R")
```
The default ```full.repro=FALSE``` checks existing downloads, and perform only a incremental update, by checking for new files on remote servers and appending data.structures tpically stired in ```./data/data.Rdata```. 

More detailed code explanation can be found in the associated ```readme.md``` in the relevant github ```master/tree``` directory (e.g. https://github.com/msandifo/reprosci/tree/master/2018/reprosci001)

